---
title: "Happiness density markdown"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, warning = FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, warning = FALSE, include=FALSE}
library(ggplot2)
library("dplyr")

setwd("~/Projects/Happiness")
df <- read.csv(file="~/Projects/Happiness/happiness_data.csv")

#take a sample of regions we are interested in
exam = df[df$Region %in% c('Western Europe','North America', 'Latin America and Caribbean', 'Eastern Asia'), ]


#take mean of values over the three years 2015-2017 by country
exam <- aggregate(exam, by=list(exam$Country, exam$Region), 
  FUN=mean, na.rm=TRUE)
exam = exam[ , !(colnames(exam) %in% c('Country','Region'))]
#temp <- df %>% group_by(Region) %>% summarize(mean_happiness = mean(Happiness.Score))

# create usable column names
colnames(exam) <- c('Country', 'Region', 'X', 'Happy_rank', 'Happy_score', 'GDPpercapita', 'Family', 'Health', 'Freedom', 'Govt', 'Generosity', 'Dystopiares', 'Year')
```

Based upon the previous analysis, it's interesting to look at the countries and regions that may not fit into the general trend, as well as the main economies.

*  selected regions: Western Europe,North America, Latin America and Caribbean, Eastern Asia
*  got mean of happy score and GDP per capita for each country over the three years (2015-2017)
*  built a density graph of regions


```{r, echo = FALSE}
ggplot (exam, aes (x = GDPpercapita, y = Happy_score, colour = Region)) + stat_density2d ()
```


The density graph suggests that the distributions of regions is mostly non-uniform. Built a graph analyzing the GDP per capita and happiness score by country (labeled as such), colored by region.

```{r, echo = FALSE}
ggplot(exam, aes(x = GDPpercapita, y = Happy_score, colour = Region, label = Country)) +
  geom_point() + 
  geom_text(size = 3, nudge_y = -.05) 

```