---
title: "Python markdown"
output:
  html_document: default
  pdf_document: default
---



```{python, engine.path="/Applications/anaconda/bin/python", echo = FALSE}
import os
os.chdir('/Users/vlad/Projects/Happiness')
import pandas as pd
import numpy as np
import matplotlib as plt


data_15 = pd.read_csv('2015.csv')
data_16 = pd.read_csv('2016.csv')
data_17 = pd.read_csv('2017.csv')
data_15['Year'] = 2015
data_16['Year'] = 2016
data_17['Year'] = 2017

data_15.drop('Standard Error', axis = 1, inplace = True)
data_16.drop(['Lower Confidence Interval', 'Upper Confidence Interval'], axis = 1, inplace = True)
data_17.drop(['Whisker.high','Whisker.low',], axis = 1, inplace = True)

#list(data_17.columns.values)

data_17.columns = ['Country','Happiness Rank','Happiness Score',
 'Economy (GDP per Capita)',
 'Family',
 'Health (Life Expectancy)',
 'Freedom',
 'Generosity',
 'Trust (Government Corruption)',
 'Dystopia Residual',
 'Year']

data_17['Region'] = ''
data_17 = data_17[list(data_16.columns.values)]

country = data_15['Country']
region = data_15['Region']
country_dict = dict(zip(country, region))
data_17.loc[:,'Region'] = data_17.loc[:,'Country']
data_17['Region'].replace(country_dict, inplace = True)

data_17.loc[data_17['Region'] == 'Belize', 'Region'] = 'Latin America and Caribbean'
data_17.loc[data_17['Region'] == 'Hong Kong S.A.R., China', 'Region'] = 'Eastern Asia'
data_17.loc[data_17['Region'] == 'Namibia', 'Region'] = 'Sub-Saharan Africa'
data_17.loc[data_17['Region'] == 'Somalia', 'Region'] = 'Middle East and Northern Africa'
data_17.loc[data_17['Region'] == 'South Sudan', 'Region'] = 'Sub-Saharan Africa'
data_17.loc[data_17['Region'] == 'Taiwan Province of China', 'Region'] = 'Eastern Asia'



df = pd.concat([data_15, data_16, data_17], axis=0, join='outer', join_axes=None, ignore_index=False,
          keys=None, levels=None, names=None, verify_integrity=False,
          copy=True)

df.to_csv('happiness_data.csv')

GDP = df.pivot_table(values = 'Economy (GDP per Capita)', index = 'Region', columns = 'Year', aggfunc = np.mean)
Happiness = df.pivot_table(values = 'Happiness Score', index = 'Region', columns = 'Year', aggfunc = np.mean)

GDP.sort_values(by =2017, ascending = True, inplace = True)
Happiness = Happiness.reindex(GDP.index)

happy = Happiness.plot(kind = 'barh', figsize=(10,5), title = 'Happiness index')
fig = happy.get_figure()
fig.tight_layout()
fig.savefig('happy.png')

gdp = GDP.plot(kind = 'barh',  figsize=(10,5), title = 'GDP per capita')
fig = gdp.get_figure()
fig.tight_layout()
fig.savefig('gdp.png')

```

This is a demo Python script that runs from R Markdown. 

*  It takes 3 files with world population data (happiness index, GDP per capita, corruption index, etc) for 2015, 2016 and 2017
*  Cleans data and makes it internally consistent
*  Saves clean data file as 'happiness_data.csv'
*  Aggregates average GDP per capita and happiness index and groups is by region
*  Creates and saves graphs
*  Creates a markdown *.html file 



```{r echo =FALSE, fig.width=10, fig.height = 5}
library(png)
library(grid)
gdp <- readPNG("~/Projects/Happiness/gdp.png")
grid.raster(gdp)
```


```{r echo =FALSE, fig.width=10, fig.height = 5}
library(png)
library(grid)
happy <- readPNG("~/Projects/Happiness/happy.png")
grid.raster(happy)
```
